The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-05 analysis/paper/paper.qmd
Add urbanism stop words found during modeling

# Add cleaned text column with removed stop words
emu_theses$text_clean <- emu_theses$text_clean |>
  str_remove_all(find_meta_stopwords(emu_theses)) |> 
  str_remove_all(urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", "tu delft", "ku leuven", "upcs barcelona", "iuav venice"))) |>
  str_remove_all(thesis_stopwords(add_stopwords = c("advisor", "prof")))

>>>>

# Add cleaned text column with removed stop words
emu_theses$text_clean <- emu_theses$text_clean |>
  str_remove_all(find_meta_stopwords(emu_theses)) |> 
  str_remove_all(urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", "tu delft", "ku leuven", "upcs barcelona", "iuav venice", 
                      "space", "spatial", "spaces", "plan", "public", "development"))) |>
  str_remove_all(thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "ning")))
